---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mane (Multi-arm N-of-1 Experiments)

<!-- badges: start -->
<!-- badges: end -->

The goal of `mane` is to provide an interface to simulate Platform-of-1 trials. It is a package that accompanies the manuscript, "Platform-of-1: A Bayesian Adaptive N-of-1 Design For Personalizing Individual Treatment Among Multiple Candidates".

## Installation

You can install the development version of mane from [GitHub](https://github.com/) with:

```{r}
# install.packages("devtools")
devtools::install_github("thecbp/mane")
```

## Example

We have implemented a Shiny dashboard that a user can use to plan out a Platform-of-1 design through the `runPlanner()` function:

```{r}
library(mane)
# runPlanner()
```

The Shiny dashboard provides an interface to simulate Platform-of-1 trials and lets a user examine the resulting operating characteristics (power, family-wise error rate) with graphs. 

Alternatively, a user may also consult the `simulation-example` vignette. This is the recommended approach if a user plans to simulate *many* trials (more than 300). RStudio has a chance to crash during the course of the simulations, so there is some extra code to help bookmark progress and continue if there is a crash.

```{r example}
# vignette("simulation-example")
```
