---
title: "Using mane to simulate multiple Platform-of-1 trials"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{simulation-example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The `simulate()` function only simulates a single Platform-of-1 design. While the Shiny app contained in `runPlanner()` can be used, there may be times where a user might need to many simulated trials (+100). The package uses Stan through the `brms` package, and its extended use can cause RStudio to crash. 

This vignette demonstrates how `mane` can be used to simulate many, many Platform-of-1 trials, while making it easy for a user to reopen the application and start back where the program left off in terms of iterations.

```{r, message = F, warnings = F }
library(tidyverse)
library(mane)
```

```{r setup}
# Create directory if not already initialized
savepath = "simulations"
if (dir.exists(savepath)) {
  dir.create(savepath)
}

# Count the number of simulations already in the designated path
start = (list.files(savepath) %>% length) + 1

n_sims = 10 # may be much bigger according to your needs

ppp = list()
for (i in 1:n_sims) {

  sim = mane::simulate(n_trts = 3,
                 n_burn_cycles = 1,
                 burn_obvs_per_period = 1,
                 adaptive_obvs_per_period = 1,
                 max_duration = 20,
                 betas = c(130, -10, 0),
                 y_sigma = 10,
                 phi = 0.25, 
                 priors = list("Intercept" = "normal(0,100)", 
                               "b" = "normal(0,100)"),
                 n_chains = 4,
                 n_iter = 3000)
  ppp[[i]] = sim

  # Save the actual simulation on your local machine
  # prefix = "sim-iter-"
  # saveRDS(sim, file = paste0(savepath, "/", prefix, i, ".rds"))
  
  print(paste0(lubridate::now(),": Finished writing iteration for sim #", i))

  # Some garbage collection
  rm(sim)
  gc()
}

saveRDS(ppp, "practice.rds")
```

```{r}
allocs = lapply(ppp, function(s) {s$allocation_probs}) %>%
  bind_rows() %>% 
  pivot_longer(cols = starts_with("X"),
               names_to = "treatment",
               values_to = "probability"
  ) %>% 
  group_by(treatment) %>% 
  summarize(
    prob = mean(probability)
  )
```

